---
title: "integration_with_published_atlases"
author: "Mette Ludwig"
date: "2022-10-14"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: inline
---


```{r}
library(anndata)
library(Seurat)
library(ggplot2)
library(ggpubr)
library(cluster)
library(parallelDist)
library(doMC)
library(Seurat)
source("/projects/mludwig/Ludwig-2021/Ludwig-2021/code/compute_sil.R")
```

# Load Seurat objects
```{r}
hippo.glia <- readRDS("/projects/mludwig/hippo_GLP1/output/Seurat_objs/hippo_glia_Seurat_obj.rds")
hippo.neurons <- readRDS("/projects/mludwig/hippo_GLP1/output/Seurat_objs/hippo_neurons_Seurat_obj.rds")
```

# Preprocess Duan et al. (Neuron, 2018)
```{r}
# Load Seurat obj
duan <- readRDS("/projects/mludwig/hippo_GLP1/output/Seurat_objs_publications/Duan_Seurat_obj.rds")

# Normalize
duan <- SCTransform(duan, verbose = FALSE)

# Define major cell type identities
duan$cell.type <- "Unknown"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(21))] <- "Pericytes"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(23))] <- "Pericytes"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(17))] <- "VLMCs"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(13))] <- "Microglia"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(3))] <- "Endothelial_cells"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(5))] <- "Endothelial_cells"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(0))] <- "Astrocytes"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(24))] <- "Astrocytes"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(18))] <- "Neurons"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(1))] <- "Neurons"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(4))] <- "Neurons"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(8))] <- "Neurons"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(10))] <- "Neurons"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(11))] <- "Neurons"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(20))] <- "Neurons"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(14))] <- "Neurons"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(15))] <- "Astrocytes"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(7))] <- "Oligodendrocytes"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(22))] <- "Oligodendrocytes"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(29))] <- "Oligodendrocytes"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(19))] <- "Oligodendrocytes"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(6))] <- "Oligodendrocytes"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(25))] <- "Oligodendrocytes"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(9))] <- "Oligodendrocytes"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(26))] <- "Ependymal_cells"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(2))] <- "Neurons"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(12))] <- "Neurons"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(16))] <- "Neurons"
duan$cell.type[which(duan$RNA_snn_res.1 %in% c(28))] <- "Neurons"

# Define minor cell type identities
duan$cell.type2 <- "Unknown"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(21))] <- "Pericytes1"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(23))] <- "Pericytes2"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(17))] <- "VLMCs"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(13))] <- "Microglia"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(3))] <- "Endothelial_cells1"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(5))] <- "Endothelial_cells2"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(0))] <- "Astrocytes1"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(24))] <- "Astrocytes2"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(18))] <- "Spock1_neurons"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(1))] <- "Nrgn_neurons1"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(4))] <- "Nrgn_neurons2"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(8))] <- "Nrgn_neurons3"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(10))] <- "Nrgn_neurons4"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(11))] <- "Nrgn_neurons5"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(20))] <- "Nrgn_neurons6"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(14))] <- "Reln_neurons"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(15))] <- "Tfap2c_cells"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(7))] <- "Mobp_oligodendrocytes1"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(22))] <- "Mobp_oligodendrocytes2"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(29))] <- "Mobp_oligodendrocytes3"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(19))] <- "Bcas1_oligodendrocytes"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(6))] <- "C1ql1_oligodendrocytes1"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(25))] <- "C1ql1_oligodendrocytes2"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(9))] <- "Enpp2_oligodendrocytes"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(26))] <- "Ependymal_cells"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(2))] <- "Unknown_neurons1"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(12))] <- "Unknown_neurons2"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(16))] <- "Unknown_neurons3"
duan$cell.type2[which(duan$RNA_snn_res.1 %in% c(28))] <- "Unknown_neurons4"

# Save
# saveRDS(duan, file = "/projects/mludwig/hippo_GLP1/output/Seurat_objs_publications/Duan_Seurat_obj_labels.rds")
```

# Transfer labels from Duan atlas
```{r}
duan <- readRDS("/projects/mludwig/hippo_GLP1/output/Seurat_objs_publications/Duan_Seurat_obj_labels.rds")

# Subset Duan atlas to glial cells
duan.glia <- subset(duan, cell.type != "Neurons")

# Normalize 
duan.glia <- SCTransform(duan.glia, verbose = F, method = "qpoisson")

# Run dimensionality reduction
duan.glia <- RunPCA(duan.glia, verbose = F)
ElbowPlot(duan.glia, ndims = 50)
duan.glia <- RunUMAP(duan.glia, dims = 1:30, n.neighbors = 50)

# Transfer labels to hippocampal glial atlas
anchors <- FindTransferAnchors(reference = duan.glia, query = hippo.glia, 
    dims = 1:30, normalization.method = "SCT")
predictions <- TransferData(anchorset = anchors, refdata = duan.glia$cell.type2, 
    dims = 1:30)

hippo.glia$duan.predictions <- predictions$predicted.id
hippo.glia$duan.score <- predictions$prediction.score.max

DimPlot(hippo.glia, group.by = "duan.predictions", label = T)
```
# Label cell type identities 
```{r}
hippo.glia$cell.type <- ""
hippo.glia$cell.type[which(hippo.glia$SCT_snn_res.0.1 %in% c(0, 2, 8))] <- "Mobp_oligodendrocytes"
hippo.glia$cell.type[which(hippo.glia$SCT_snn_res.0.1 %in% c(1))] <- "Astrocytes"
hippo.glia$cell.type[which(hippo.glia$SCT_snn_res.0.1 %in% c(3))] <- "Microglia"
hippo.glia$cell.type[which(hippo.glia$SCT_snn_res.0.1 == 7)] <- "Unknown_glia"
hippo.glia$cell.type[which(hippo.glia$SCT_snn_res.1 == 21)] <- "Pericytes2"
hippo.glia$cell.type[which(hippo.glia$SCT_snn_res.1 == 25)] <- "VLMCs"
hippo.glia$cell.type[which(hippo.glia$SCT_snn_res.0.1 %in% c(5) &
                            hippo.glia$SCT_snn_res.1 == "18")] <- "Pericytes1"
hippo.glia$cell.type[which(hippo.glia$SCT_snn_res.0.1 %in% c(5) &
                            hippo.glia$SCT_snn_res.1 != "18")] <- "Endothelial_cells"
hippo.glia$cell.type[which(hippo.glia$SCT_snn_res.0.1 %in% c(4) &
                              hippo.glia$SCT_snn_res.1 != 19)] <- "C1ql1_oligodendrocytes"
hippo.glia$cell.type[which(hippo.glia$SCT_snn_res.0.1 %in% c(4) &
                              hippo.glia$SCT_snn_res.1 == 19)] <- "Bcas1_oligodendrocytes"

hippo.glia$cell.type <- factor(hippo.glia$cell.type, levels = c("Astrocytes", "Bcas1_oligodendrocytes",
                                                                "C1ql1_oligodendrocytes", "Endothelial_cells",
                                                                "Microglia", "Mobp_oligodendrocytes",
                                                                "Pericytes1", "Pericytes2", 
                                                                "Unknown_glia", "VLMCs"))
```

# Compute silhouette scores to identify optimal clustering resolution
```{r}
resolution <- seq(0.1, 1, 0.1)

pc <- hippo.glia@reductions$pca@cell.embeddings[, 1:30]
distance <- parDist(pc, method = "euclidean")

cluster.id <- as.character(hippo.glia@meta.data[, "cell.type"])
silhouette.cell.type <- compute.sil(x = cluster.id, dist = distance)

print(mean(silhouette.cell.tyoe))

stability <- data.frame(matrix(NA, nrow = ncol(hippo.glia), ncol = length(resolution)))
colnames(stability) <- resolution
rownames(stability) <- colnames(hippo.glia)

for(i in 1:length(resolution)) {
  print(i)

  hippo.glia <- FindClusters(object = hippo.glia, resolution = resolution[i],
                         verbose = F)
  cluster.id <- as.numeric(as.character(hippo.glia@meta.data[, paste0("SCT_snn_res.", resolution[i])]))

  silhouette <- compute.sil(x = cluster.id, dist = distance)

  print(mean(silhouette))

  stability[,i] <- silhouette

}
stability <- cbind(cell.type = silhouette.cell.type, stability)

# Save
# saveRDS(stability, file = "/projects/mludwig/hippo_GLP1/output/Seurat_objs/silhouette_glia.rds")
stability <- readRDS("/projects/mludwig/hippo_GLP1/output/Seurat_objs/silhouette_glia.rds")

# Plot
stability$cell <- rownames(stability)
stability.melt <- reshape2::melt(stability, id.vars = "cell")
stability.melt$variable <- gsub("cell.type", "Duan labels", stability.melt$variable)

ggplot(stability.melt) +
  geom_boxplot(aes(x = variable, y = value), outlier.shape = NA, fill = "darkcyan") +
  theme_pubr() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("Resolution") + ylab("Silhouette score") +
  scale_y_continuous(limits = c(-1, 1), breaks = seq(-1, 1, 0.25))
```

# Preprocess Posner et al. (Current Opinion in Immunology, 2022)
```{r}
# # Load anndata obj
# posner.h5ad <- read_h5ad("/scratch/mlf210/CNSbordercellatlas_Dec22.h5ad")
# 
# # Convert anndata obj to Seurat obj
# posner.counts <- rbind(as.matrix(posner.h5ad[["X"]][1:65000, ]),
#                        as.matrix(posner.h5ad[["X"]][65001:nrow(posner.h5ad[["X"]]), ]))
#  
# posner.counts <- t(posner.counts)
#  
# posner <- CreateSeuratObject(posner.counts, meta.data = posner.h5ad[["obs"]])
# rm(posner.counts)
# rm(posner.h5ad)
#  
# # Normalize 
# posner <- SCTransform(posner, verbose = F, method = "qpoisson")
# 
# # Run dimensionality reduction
# posner <- RunPCA(posner, verbose = F)
# ElbowPlot(posner, ndims = 50)
# posner <- RunUMAP(posner, dims = 1:30, n.neighbors = 50)
# 
# # Run clustering
# posner <- FindNeighbors(posner, dims = 1:30, k.param = 50)
# posner <- FindClusters(posner, resolution = 0.1, verbose = F)
# 
# # Save
# saveRDS(posner, file = "projects/mludwig/hippo_GLP1/output/Seurat_objs_publications/Posner_Seurat_obj.rds")
```


# Transfer labels from Posner atlas
```{r}
posner <- readRDS("/projects/mludwig/hippo_GLP1/output/Seurat_objs_publications/Posner_Seurat_obj.rds")

anchors <- FindTransferAnchors(reference = posner, query = hippo.glia, 
    dims = 1:30, normalization.method = "SCT")
predictions <- TransferData(anchorset = anchors, refdata = posner$celltype, 
    dims = 1:30)
saveRDS(predictions, file = "/projects/mludwig/hippo_GLP1/output/Seurat_objs/Posner_predictions.rds")

hippo.glia$posner.predictions <- predictions$predicted.id
hippo.glia$posner.score <- predictions$prediction.score.max

DimPlot(hippo.glia, group.by = "posner.predictions", label = T)

# Update the labels
hippo.glia$cell.type2 <- hippo.glia$cell.type
hippo.glia$cell.type2 <- gsub("Unknown_glia", "Neutrophils", hippo.glia$cell.type2)

hippo.glia$cell.type2 <- factor(hippo.glia$cell.type2, levels = c("Astrocytes",
                                                                  "Bcas1_oligodendrocytes",
                                                                  "C1ql1_oligodendrocytes",
                                                                  "Endothelial_cells",
                                                                  "Microglia", 
                                                                  "Mobp_oligodendrocytes",
                                                                  "Neutrophils", 
                                                                  "Pericytes1", 
                                                                  "Pericytes2", 
                                                                  "VLMCs"))
```


# Save
```{r}
hippo.glia@meta.data  <- hippo.glia@meta.data[, c("nCount_RNA", "nFeature_RNA", 
                                                  "nCount_SCT", "nFeature_SCT",
                                                  "percent.mt", "pool", "hash.ID", 
                                                  "treatment", "drug", "time", "run", 
                                                  "SCT_snn_res.0.1", "SCT_snn_res.1",
                                                  "duan.predictions", "duan.score",
                                                  "cell.type", "cell.type2")]
# saveRDS(hippo.glia, 
#         file = "/projects/mludwig/hippo_GLP1/output/Seurat_objs/hippo_glia_Seurat_obj_labels.rds")
```


# Preprocess Smart-seq data Yao et al. (Cell, 2021)
```{r}
# Load Seurat object
load("/projects/mludwig/hippo_GLP1/data/2021_Yao/Seurat.ss.rda")

# Subset yao atlas to hippocampal neurons
yao <- subset(ss.seurat, region_label == "HIP" & class_label != "Non-Neuronal")

# Normalize 
yao <- SCTransform(yao, verbose = F, method = "qpoisson")

# Run dimensionality reduction
yao <- RunPCA(yao, verbose = F)
ElbowPlot(yao, ndims = 50)
yao <- RunUMAP(yao, dims = 1:30, n.neighbors = 50)

# Run clustering
yao <- FindNeighbors(yao, dims = 1:30, k.param = 50)
yao <- FindClusters(yao, resolution = 0.1, verbose = F)

DimPlot(yao, group.by = "class_label")
DimPlot(yao, group.by = "subclass_label", label = T)
DimPlot(yao, group.by = "region_label", label = T)
```

# Transfer labels from Yao data
```{r}
anchors <- FindTransferAnchors(reference = yao, query = hippo.neurons, 
    dims = 1:30, normalization.method = "SCT")
predictions <- TransferData(anchorset = anchors, refdata = yao$subclass_label, 
    dims = 1:30)

hippo.neurons$yao.predictions <- predictions$predicted.id
hippo.neurons$yao.score <- predictions$predicted.id

DimPlot(hippo.neurons, group.by = "yao.predictions", label = T) 
DimPlot(hippo.neurons, group.by = "cell.type", label = T)
DimPlot(hippo.neurons, group.by = "SCT_snn_res.1", label = T)
```

# Label cell type identities 
```{r}
hippo.neurons$cell.type <- paste0("Neurons", hippo.neurons$SCT_snn_res.0.1)
hippo.neurons$cell.type <- factor(hippo.neurons$cell.type, 
                                  levels =  paste0("Neurons", sort(unique(hippo.neurons$SCT_snn_res.0.1))))


hippo.neurons$cell.type2 <- ""
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.1 == 17)] <- "Vip"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.1 == 15)] <- "Sncg"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.1 %in% c(14, 22))] <- "Lamp5"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.1 == 12)] <- "Sst"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.1 == 16)] <- "Pvalb"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.1 %in% c(0, 1, 2, 4, 5,
                                                                  9, 13, 21, 24))] <- "DG"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.1 %in% c(3, 6, 8))] <- "CA1"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.1 %in% c(7, 11, 18, 23))] <- "CA3"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.1 == 19)] <- "SUB"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.1 == 20)] <- "ProS"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.1 == 10)] <- "CA2/CA3"

DimPlot(hippo.neurons, group.by = "cell.type2", label = T)
```


# Compute silhouette scores to identify optimal clustering resolution
```{r}
resolution <- seq(0.1, 1, 0.1)

pc <- hippo.neurons@reductions$pca@cell.embeddings[, 1:30]
distance <- parDist(pc, method = "euclidean")

cluster.id <- as.character(hippo.neurons@meta.data[, "cell.type2"])
silhouette.cell.type <- compute.sil(x = cluster.id, dist = distance)


stability <- data.frame(matrix(NA, nrow = ncol(hippo.neurons), ncol = length(resolution)))
colnames(stability) <- resolution
rownames(stability) <- colnames(hippo.neurons)

for(i in 1:length(resolution)) {
  print(i)

  hippo.neurons <- FindClusters(object = hippo.neurons, resolution = resolution[i],
                         verbose = F)
  cluster.id <- as.numeric(as.character(hippo.neurons@meta.data[, paste0("SCT_snn_res.", resolution[i])]))

  silhouette <- compute.sil(x = cluster.id, dist = distance)

  print(mean(silhouette))

  stability[,i] <- silhouette

}

stability <- cbind(cell.type = silhouette.cell.type, stability)

# saveRDS(stability, file = "/projects/mludwig/hippo_GLP1/output/Seurat_objs/silhouette_neurons.rds")
stability <- readRDS("/projects/mludwig/hippo_GLP1/output/Seurat_objs/silhouette_neurons.rds")

stability$cell <- rownames(stability)
stability.melt <- reshape2::melt(stability, id.vars = "cell")
stability.melt$variable <- gsub("cell.type", "Yao labels", stability.melt$variable)

ggplot(stability.melt) +
  geom_boxplot(aes(x = variable, y = value), outlier.shape = NA, fill = "darkcyan") +
  theme_pubr() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("Resolution") + ylab("Silhouette score") +
  scale_y_continuous(limits = c(-1, 1), breaks = seq(-1, 1, 0.25))

```

# Update cell type labels at optimal clustering resolution
```{r}
cellex <- read.csv(gzfile("/projects/mludwig/hippo_GLP1/output/cellex/output/hippo_neurons_mm.esmu.csv.gz"), row.names = 1)

neuron.markers <- data.frame(matrix(NA, nrow = length(levels(hippo.neurons$cell.type)), ncol = 4))
colnames(neuron.markers) <- c("cell.type", "marker1", "marker2", "marker3")
neuron.markers$cell.type <- levels(hippo.neurons$cell.type)
  
# Plot marker gene expression
for (i in 1:nrow(neuron.markers)) {
  
  neuron.cell.type <- neuron.markers$cell.type[i]
  
  
  idx <- which(hippo.neurons$cell.type == neuron.cell.type)
    
  genes.ordered <- rownames(cellex)[order(cellex[, neuron.cell.type], decreasing = T)]
  genes.ordered <- genes.ordered[!(grepl("^Gm[0-9]|^ENSMUS|[0-9]Rik$", genes.ordered))]
  
  z <- 2
  for (j in genes.ordered) {
    
    nonzero.counts <- which(hippo.neurons@assays$RNA@counts[j, idx] != 0)
    nonzero.pct <- length(nonzero.counts) / length(idx) * 100
    
    if (nonzero.pct >= 25) {
      neuron.markers[i, z] <- j
      z <- z + 1
    }
    if (z > 4)  {
      break
    }
  }
}

neuron.markers

hippo.neurons$cell.type2 <- ""
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.0.1 == 0)] <- "Glis3_DG_neurons"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.0.1 == 1)] <- "Satb2_CA1_neurons"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.0.1 == 2)] <- "Cd109_CA3_neurons"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.0.1 == 3)] <- "Crhbp_MGE_neurons"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.0.1 == 4)] <- "Lhx1_CA2/CA3_neurons"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.0.1 == 5)] <- "Htr3a_CGE_neurons"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.0.1 == 6)] <- "Igfbpl1_DG_neurons"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.0.1 == 7)] <- "Sfta3-ps_CGE_neurons"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.0.1 == 8)] <- "Csf2rb2_CA3_neurons"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.0.1 == 9)] <- "Abca12_Subiculum_neurons"
hippo.neurons$cell.type2[which(hippo.neurons$SCT_snn_res.0.1 == 10)] <- "Nts_Prosubiculum_neurons"
```

# Save
```{r}
# saveRDS(hippo.neurons, 
#         file = "/projects/mludwig/hippo_GLP1/output/Seurat_objs/hippo_neurons_Seurat_obj_labels.rds")
```
