---
title: "milo_analysis_glia"
author: "Mette Ludwig"
date: "2022-10-14"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: inline
---


```{r}
library(miloR)
library(SingleCellExperiment)
library(scater)
library(scran)
library(dplyr)
library(patchwork)
library(Seurat)
```

# Load Seurat objects
```{r}
hippo.glia <- readRDS("/projects/mludwig/hippo_GLP1/output/Seurat_objs/hippo_glia_Seurat_obj_labels.rds")
hippo.glia$cell.type <- hippo.glia$cell.type2

DVC.glia <- readRDS("/projects/mludwig/hippo_GLP1/output/Seurat_objs/DVC_glia_Seurat_obj_labels.rds")
```



### Perform milo analysis for hippocampal glial cells (veh-LPS vs. veh-PBS) ###
```{r}
# Subset Seurat object
groups <- c("Veh-PBS", "Veh-LPS")
hippo.veh <- subset(hippo.glia, drug %in% groups)

# Run PCA
hippo.veh <- RunPCA(hippo.veh, verbose = F)

# Select number of PCs
ElbowPlot(hippo.veh, ndims = 50)

DimPlot(hippo.veh, group.by = "cell.type", shuffle = T)
DimPlot(hippo.veh, group.by = "drug", shuffle = T)
DimPlot(hippo.veh, group.by = "time", shuffle = T)
```

# Create milo object
```{r}
hippo.veh.sce <- as.SingleCellExperiment(hippo.veh, assay = "SCT")
hippo.veh.milo <- Milo(hippo.veh.sce)

reducedDim(hippo.veh.milo, "UMAP") <- reducedDim(hippo.veh.sce, "UMAP")
reducedDim(hippo.veh.milo, "PCA") <- reducedDim(hippo.veh.sce, "PCA")
plotReducedDim(hippo.veh.milo, colour_by = "drug", dimred = "UMAP") 
```

# Construct KNN graph
```{r}
k <- 50
d <- 30
hippo.veh.milo <- buildGraph(hippo.veh.milo, k = k, d = d, reduced.dim = "PCA")
```

# Define representative neighbourhoods on the KNN graph
```{r}
hippo.veh.milo <- makeNhoods(hippo.veh.milo, prop = 0.1, k = k, d = d, refined = TRUE, reduced_dims = "PCA")
plotNhoodSizeHist(hippo.veh.milo)
```

# Count cells in neighbourhoods
```{r}
hippo.veh.milo <- countCells(hippo.veh.milo, meta.data = as.data.frame(colData(hippo.veh.milo)), 
                             samples = "hash.ID")
head(nhoodCounts(hippo.veh.milo))
```

# Compute neighbourhood connectivity
```{r}
hippo.veh.milo <- calcNhoodDistance(hippo.veh.milo, d = d, reduced.dim = "PCA")
```

# Define experimental design
```{r}
design <- data.frame(colData(hippo.veh.milo))[, c("hash.ID", "drug", "time")]

design <- distinct(design)
design$drug <- factor(design$drug, levels = groups)
rownames(design) <- design$hash.ID
```

# Test
```{r}
model <- model.matrix(~ drug, data = design)
colnames(model) <- make.names(colnames(model))
da.results <- testNhoods(hippo.veh.milo, design = model, design.df = design, model.contrasts = "drugVeh.LPS")

da.results %>% arrange(PValue) %>% head(n = 50)
length(which(da.results$SpatialFDR < 0.05))
```

# InspectDA testing results
```{r}
hippo.veh$Neighboorhods <- "Non-altered"
idx <- which(da.results$SpatialFDR < 0.05)

if (length(idx) > 0) {
  hippo.veh$Neighboorhods[which(apply(hippo.veh.milo@nhoods[, idx], 1, sum) > 0)] <- "Altered"
  
}

DimPlot(hippo.veh, group.by = "Neighboorhods")

ggplot(da.results, aes(PValue)) + geom_histogram(bins=50)

ggplot(da.results, aes(logFC, -log10(SpatialFDR))) + 
  geom_point() +
  geom_hline(yintercept = -log10(0.05)) # Mark significance threshold (5% FDR)
```

# Build and plot neighborhood graph
```{r}
hippo.veh.milo <- buildNhoodGraph(hippo.veh.milo)

plotNhoodGraphDA(hippo.veh.milo, da.results, layout = "UMAP", alpha = 0.1, size = 2)
```

# Assign a cell type label to each neighbourhood by finding the most abundant cell type within cells in each neighbourhood
```{r}
da.results <- annotateNhoods(hippo.veh.milo, da.results, coldata_col = "cell.type")
head(da.results)
```

W# hile neighbourhoods tend to be homogeneous, we can define a threshold for `celltype_fraction` to exclude neighbourhoods that are a mix of cell types
```{r}
ggplot(da.results, aes(cell.type_fraction)) + geom_histogram(bins=50)

da.results$cell.type <- ifelse(da.results$cell.type_fraction < 0.7, "Mixed", da.results$cell.type)

plotDAbeeswarm(da.results, group.by = "cell.type")

cell.type.abundance <- data.frame(matrix(NA, nrow = length(unique(da.results$cell.type)), ncol = 2))
colnames(cell.type.abundance) <- c("cell.type", "abundance")
cell.type.abundance$cell.type <- unique(da.results$cell.type)

for (i in 1:nrow(cell.type.abundance)) {
  cell.type <- cell.type.abundance$cell.type[i]
  
  significant <- length(which(da.results$cell.type == cell.type & da.results$SpatialFDR < 0.05)) 
  all <- length(which(da.results$cell.type == cell.type)) 

  cell.type.abundance$abundance[i] <- significant / all
  
}

cell.type.abundance[order(cell.type.abundance$abundance, decreasing = T),]
```

# Save milo object
```{r}
# saveRDS(hippo.veh.milo, file = "/projects/mludwig/hippo_GLP1/output/milo_objs/hippo_glia_veh_milo_obj.rds")
```



### Perform milo analysis for hippocampal glial cells (sema-LPS vs. veh-LPS) ###
```{r}
# Subset seurat object
groups <- c("Veh-LPS", "Sema-LPS")
hippo.LPS <- subset(hippo.glia, drug %in% groups)

# Run PCA
hippo.LPS <- RunPCA(hippo.LPS, verbose = F)

# Select number of PCs
ElbowPlot(hippo.LPS, ndims = 50)

DimPlot(hippo.LPS, group.by = "cell.type", shuffle = T)
DimPlot(hippo.LPS, group.by = "drug", shuffle = T)
DimPlot(hippo.LPS, group.by = "time", shuffle = T)
```

# Create milo object
```{r}
hippo.LPS.sce <- as.SingleCellExperiment(hippo.LPS, assay = "SCT")
hippo.LPS.milo <- Milo(hippo.LPS.sce)

reducedDim(hippo.LPS.milo, "UMAP") <- reducedDim(hippo.LPS.sce, "UMAP")
reducedDim(hippo.LPS.milo, "PCA") <- reducedDim(hippo.LPS.sce, "PCA")
plotReducedDim(hippo.LPS.milo, colour_by = "drug", dimred = "UMAP") 
```

# Construct KNN graph
```{r}
k <- 50
d <- 30
hippo.LPS.milo <- buildGraph(hippo.LPS.milo, k = k, d = d, reduced.dim = "PCA")
```

# Define representative neighbourhoods on the KNN graph
```{r}
hippo.LPS.milo <- makeNhoods(hippo.LPS.milo, prop = 0.1, k = k, d = d, refined = TRUE, reduced_dims = "PCA")
plotNhoodSizeHist(hippo.LPS.milo)
```

# Count cells in neighbourhoods
```{r}
hippo.LPS.milo <- countCells(hippo.LPS.milo, meta.data = as.data.frame(colData(hippo.LPS.milo)), 
                             samples = "hash.ID")
head(nhoodCounts(hippo.LPS.milo))
```

# Compute neighbourhood connectivity
```{r}
hippo.LPS.milo <- calcNhoodDistance(hippo.LPS.milo, d = d, reduced.dim = "PCA")
```

# Define experimental design
```{r}
design <- data.frame(colData(hippo.LPS.milo))[, c("hash.ID", "drug", "time")]

design <- distinct(design)
design$drug <- factor(design$drug, levels = groups)
rownames(design) <- design$hash.ID
```

# Test
```{r}
model <- model.matrix(~ drug, data = design)
colnames(model) <- make.names(colnames(model))
da.results <- testNhoods(hippo.LPS.milo, design = model, design.df = design, model.contrasts = "drugSema.LPS")

da.results %>% arrange(PValue) %>% head(n = 50)
length(which(da.results$SpatialFDR < 0.05))
```

# Inspect DA testing results
```{r}
hippo.LPS$Neighboorhods <- "Non-altered"
idx <- which(da.results$SpatialFDR < 0.05)

if (length(idx) > 0) {
  hippo.LPS$Neighboorhods[which(apply(hippo.LPS.milo@nhoods[, idx], 1, sum) > 0)] <- "Altered"
  
}
DimPlot(hippo.LPS, group.by = "Neighboorhods")

ggplot(da.results, aes(PValue)) + geom_histogram(bins=50)

ggplot(da.results, aes(logFC, -log10(SpatialFDR))) + 
  geom_point() +
  geom_hline(yintercept = -log10(0.05)) # Mark significance threshold (5% FDR)
```

# Build and plot neighborhood graph
```{r}
hippo.LPS.milo <- buildNhoodGraph(hippo.LPS.milo)

plotNhoodGraphDA(hippo.LPS.milo, da.results, layout = "UMAP", alpha = 0.1, size = 2)
```

# Assign a cell type label to each neighbourhood by finding the most abundant cell type within cells in each neighbourhood
```{r}
da.results <- annotateNhoods(hippo.LPS.milo, da.results, coldata_col = "cell.type")
head(da.results)
```

# While neighbourhoods tend to be homogeneous, we can define a threshold for `celltype_fraction` to exclude neighbourhoods that are a mix of cell types 
```{r}
ggplot(da.results, aes(cell.type_fraction)) + geom_histogram(bins=50)

da.results$cell.type <- ifelse(da.results$cell.type_fraction < 0.7, "Mixed", da.results$cell.type)
plotDAbeeswarm(da.results, group.by = "cell.type")

cell.type.abundance <- data.frame(matrix(NA, nrow = length(unique(da.results$cell.type)), ncol = 2))
colnames(cell.type.abundance) <- c("cell.type", "abundance")
cell.type.abundance$cell.type <- unique(da.results$cell.type)

for (i in 1:nrow(cell.type.abundance)) {
  cell.type <- cell.type.abundance$cell.type[i]
  
  significant <- length(which(da.results$cell.type == cell.type & da.results$SpatialFDR < 0.05)) 
  all <- length(which(da.results$cell.type == cell.type)) 

  cell.type.abundance$abundance[i] <- significant / all
  
}

cell.type.abundance[order(cell.type.abundance$abundance, decreasing = T),]
```

# Save milo object
```{r}
# saveRDS(hippo.LPS.milo, file = "/projects/mludwig/hippo_GLP1/output/milo_objs/hippo_glia_LPS_milo_obj.rds")
```



### Perform milo analysis for DVC glial cells (veh-LPS vs. veh-PBS) ###
```{r}
# Subset Seurat object
groups <- c("Veh-PBS", "Veh-LPS")
DVC.veh <- subset(DVC.glia, drug %in% groups)

# Run PCA
DVC.veh <- RunPCA(DVC.veh, verbose = F)

# Select number of PCs
ElbowPlot(DVC.veh, ndims = 50)

DimPlot(DVC.veh, group.by = "cell.type", shuffle = T)
DimPlot(DVC.veh, group.by = "drug", shuffle = T)
DimPlot(DVC.veh, group.by = "time", shuffle = T)
```

# Create milo object
```{r}
DVC.veh.sce <- as.SingleCellExperiment(DVC.veh, assay = "SCT")
DVC.veh.milo <- Milo(DVC.veh.sce)

reducedDim(DVC.veh.milo, "UMAP") <- reducedDim(DVC.veh.sce, "UMAP")
reducedDim(DVC.veh.milo, "PCA") <- reducedDim(DVC.veh.sce, "PCA")
plotReducedDim(DVC.veh.milo, colour_by = "drug", dimred = "UMAP") 
```

# Construct KNN graph
```{r}
k <- 50
d <- 30
DVC.veh.milo <- buildGraph(DVC.veh.milo, k = k, d = d, reduced.dim = "PCA")
```

# Define representative neighbourhoods on the KNN graph
```{r}
DVC.veh.milo <- makeNhoods(DVC.veh.milo, prop = 0.1, k = k, d = d, refined = TRUE, reduced_dims = "PCA")
plotNhoodSizeHist(DVC.veh.milo)
```

# Count cells in neighbourhoods
```{r}
DVC.veh.milo <- countCells(DVC.veh.milo, meta.data = as.data.frame(colData(DVC.veh.milo)), 
                             samples = "hash.ID")
head(nhoodCounts(DVC.veh.milo))
```

# Compute neighbourhood connectivity
```{r}
DVC.veh.milo <- calcNhoodDistance(DVC.veh.milo, d = d, reduced.dim = "PCA")
```

# Define experimental design
```{r}
design <- data.frame(colData(DVC.veh.milo))[, c("hash.ID", "drug", "time")]

design <- distinct(design)
design$drug <- factor(design$drug, levels = groups)
rownames(design) <- design$hash.ID
```

# Test
```{r}
model <- model.matrix(~ drug, data = design)
colnames(model) <- make.names(colnames(model))
da.results <- testNhoods(DVC.veh.milo, design = model, design.df = design, model.contrasts = "drugVeh.LPS")

da.results %>% arrange(PValue) %>% head(n = 50)
length(which(da.results$SpatialFDR < 0.05))
```

# Inspect DA testing results
```{r}
DVC.veh$Neighboorhods <- "Non-altered"
idx <- which(da.results$SpatialFDR < 0.05)

if (length(idx) > 0) {
  DVC.veh$Neighboorhods[which(apply(DVC.veh.milo@nhoods[, idx], 1, sum) > 0)] <- "Altered"
  
}
DimPlot(DVC.veh, group.by = "Neighboorhods")

ggplot(da.results, aes(PValue)) + geom_histogram(bins=50)

ggplot(da.results, aes(logFC, -log10(SpatialFDR))) + 
  geom_point() +
  geom_hline(yintercept = -log10(0.05)) # Mark significance threshold (5% FDR)
```

# Build and plot neighborhood graph
```{r}
DVC.veh.milo <- buildNhoodGraph(DVC.veh.milo)

plotNhoodGraphDA(DVC.veh.milo, da.results, layout = "UMAP", alpha = 0.1, size = 2)
```

# Assign a cell type label to each neighbourhood by finding the most abundant cell type within cells in each neighbourhood
```{r}
da.results <- annotateNhoods(DVC.veh.milo, da.results, coldata_col = "cell.type")
head(da.results)
```

# While neighbourhoods tend to be homogeneous, we can define a threshold for `celltype_fraction` to exclude neighbourhoods that are a mix of cell types
```{r}
ggplot(da.results, aes(cell.type_fraction)) + geom_histogram(bins=50)

da.results$cell.type <- ifelse(da.results$cell.type_fraction < 0.7, "Mixed", da.results$cell.type)

plotDAbeeswarm(da.results, group.by = "cell.type")

cell.type.abundance <- data.frame(matrix(NA, nrow = length(unique(da.results$cell.type)), ncol = 2))
colnames(cell.type.abundance) <- c("cell.type", "abundance")
cell.type.abundance$cell.type <- unique(da.results$cell.type)

for (i in 1:nrow(cell.type.abundance)) {
  cell.type <- cell.type.abundance$cell.type[i]
  
  significant <- length(which(da.results$cell.type == cell.type & da.results$SpatialFDR < 0.05)) 
  all <- length(which(da.results$cell.type == cell.type)) 

  cell.type.abundance$abundance[i] <- significant / all
  
}

cell.type.abundance[order(cell.type.abundance$abundance, decreasing = T),]
```

# Save milo object
```{r}
# saveRDS(DVC.veh.milo, file = "/projects/mludwig/hippo_GLP1/output/milo_objs/DVC_glia_veh_milo_obj.rds")
```



### Perform milo analysis for DVC glial cells (sema-LPS vs. veh-LPS) ###
```{r}
# Subset seurat object
groups <- c("Veh-LPS", "Sema-LPS")
DVC.LPS <- subset(DVC.glia, drug %in% groups)

# Run PCA
DVC.LPS <- RunPCA(DVC.LPS, verbose = F)

# Select number of PCs
ElbowPlot(DVC.LPS, ndims = 50)

DimPlot(DVC.LPS, group.by = "cell.type", shuffle = T)
DimPlot(DVC.LPS, group.by = "drug", shuffle = T)
DimPlot(DVC.LPS, group.by = "time", shuffle = T)
```

# Create milo object
```{r}
DVC.LPS.sce <- as.SingleCellExperiment(DVC.LPS, assay = "SCT")
DVC.LPS.milo <- Milo(DVC.LPS.sce)

reducedDim(DVC.LPS.milo, "UMAP") <- reducedDim(DVC.LPS.sce, "UMAP")
reducedDim(DVC.LPS.milo, "PCA") <- reducedDim(DVC.LPS.sce, "PCA")
plotReducedDim(DVC.LPS.milo, colour_by = "drug", dimred = "UMAP") 
```

# Construct KNN graph
```{r}
k <- 50
d <- 30
DVC.LPS.milo <- buildGraph(DVC.LPS.milo, k = k, d = d, reduced.dim = "PCA")
```

# Define representative neighbourhoods on the KNN graph
```{r}
DVC.LPS.milo <- makeNhoods(DVC.LPS.milo, prop = 0.1, k = k, d = d, refined = TRUE, reduced_dims = "PCA")
plotNhoodSizeHist(DVC.LPS.milo)
```

# Count cells in neighbourhoods
```{r}
DVC.LPS.milo <- countCells(DVC.LPS.milo, meta.data = as.data.frame(colData(DVC.LPS.milo)), 
                             samples = "hash.ID")
head(nhoodCounts(DVC.LPS.milo))
```

# Compute neighbourhood connectivity
```{r}
DVC.LPS.milo <- calcNhoodDistance(DVC.LPS.milo, d = d, reduced.dim = "PCA")
```

# Define experimental design
```{r}
design <- data.frame(colData(DVC.LPS.milo))[, c("hash.ID", "drug", "time")]

design <- distinct(design)
design$drug <- factor(design$drug, levels = groups)
rownames(design) <- design$hash.ID
```

# Test
```{r}
model <- model.matrix(~ drug, data = design)
colnames(model) <- make.names(colnames(model))
da.results <- testNhoods(DVC.LPS.milo, design = model, design.df = design, model.contrasts = "drugSema.LPS")

da.results %>% arrange(PValue) %>% head(n = 50)
length(which(da.results$SpatialFDR < 0.05))
```

# Inspect DA testing results
```{r}
DVC.LPS$Neighboorhods <- "Non-altered"
idx <- which(da.results$SpatialFDR < 0.05)

if (length(idx) > 0) {
  DVC.LPS$Neighboorhods[which(apply(DVC.LPS.milo@nhoods[, idx], 1, sum) > 0)] <- "Altered"
  
}
DimPlot(DVC.LPS, group.by = "Neighboorhods")

ggplot(da.results, aes(PValue)) + geom_histogram(bins=50)

ggplot(da.results, aes(logFC, -log10(SpatialFDR))) + 
  geom_point() +
  geom_hline(yintercept = -log10(0.05)) # Mark significance threshold (5% FDR)
```

# Build and plot neighborhood graph
```{r}
DVC.LPS.milo <- buildNhoodGraph(DVC.LPS.milo)

plotNhoodGraphDA(DVC.LPS.milo, da.results, layout = "UMAP", alpha = 0.1, size = 2)
```

# Assign a cell type label to each neighbourhood by finding the most abundant cell type within cells in each neighbourhood
```{r}
da.results <- annotateNhoods(DVC.LPS.milo, da.results, coldata_col = "cell.type")
head(da.results)
```

# While neighbourhoods tend to be homogeneous, we can define a threshold for `celltype_fraction` to exclude neighbourhoods that are a mix of cell types
```{r}
ggplot(da.results, aes(cell.type_fraction)) + geom_histogram(bins=50)

da.results$cell.type <- ifelse(da.results$cell.type_fraction < 0.7, "Mixed", da.results$cell.type)
plotDAbeeswarm(da.results, group.by = "cell.type")

cell.type.abundance <- data.frame(matrix(NA, nrow = length(unique(da.results$cell.type)), ncol = 2))
colnames(cell.type.abundance) <- c("cell.type", "abundance")
cell.type.abundance$cell.type <- unique(da.results$cell.type)

for (i in 1:nrow(cell.type.abundance)) {
  cell.type <- cell.type.abundance$cell.type[i]
  
  significant <- length(which(da.results$cell.type == cell.type & da.results$SpatialFDR < 0.05)) 
  all <- length(which(da.results$cell.type == cell.type)) 

  cell.type.abundance$abundance[i] <- significant / all
  
}

cell.type.abundance[order(cell.type.abundance$abundance, decreasing = T),]
```

# Save milo object
```{r}
# saveRDS(DVC.LPS.milo, file = "/projects/mludwig/hippo_GLP1/output/milo_objs/DVC_glia_LPS_milo_obj.rds")
```

