---
title: "scDRS_analysis"
author: "Mette Ludwig"
date: "2022-10-14"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: inline
---

# Convert Seurat objects to h5ad file
```{r}
library(Seurat)
library(anndata)
library(Matrix)

hippo <- readRDS("/projects/mludwig/hippo_GLP1/output/Seurat_objs/hippo_Seurat_obj_labels.rds")

counts <- as(hippo@assays$RNA@counts, "sparseMatrix")
meta <- hippo@meta.data
var <- data.frame(type =  as.integer(seq(1, nrow(counts))), row.names = rownames(counts))


adata <- AnnData(X = t(counts),
                 obs = meta,
                 var = var)

write_h5ad(adata, file = "/home/cbmr/mlf210/scDRS/anndata_objs/hippo_labels.h5ad")
```


# Map Entrez ID in MAGMA file to gene ID 
```{r}
# Load mapping data
mapping.data3 <- read.csv("/projects/mludwig/DVC/data/gene_info/NCBI37.3.gene.loc",
                          sep = "", header = F)
colnames(mapping.data3) <- c("ENTREZID", "chr", "start", "end", "strand", "ALIAS")


# Load MAGMA gene-level statistics
MAGMA.AD <- read.table("/projects/mludwig/hippo_GLP1/data/GWAS/AD_bellenguez.genes.out", header = T)
head(MAGMA.AD)

# Map to gene symbol
MAGMA.AD$ALIAS <- mapping.data3$ALIAS[match(MAGMA.AD$GENE, mapping.data3$ENTREZID)]
MAGMA.AD <- MAGMA.AD[c("ALIAS", "ZSTAT")]
colnames(MAGMA.AD) <- c("GENE", "AD")

write.table(MAGMA.AD, file = "/projects/mludwig/hippo_GLP1/data/GWAS/AD_bellenguez_scDRS_genes.in",
            row.names = F, quote = F, sep = "\t")


# Load MAGMA gene-level statistics
MAGMA.BMI <- read.table("/projects/mludwig/hippo_GLP1/data/GWAS/BMI_loh.genes.out", header = T)
head(MAGMA.BMI)

# Map to gene symbol
MAGMA.BMI$ALIAS <- mapping.data3$ALIAS[match(MAGMA.BMI$GENE, mapping.data3$ENTREZID)]
MAGMA.BMI <- MAGMA.BMI[c("ALIAS", "ZSTAT")]
colnames(MAGMA.BMI) <- c("GENE", "BMI")

write.table(MAGMA.BMI, file = "/projects/mludwig/hippo_GLP1/data/GWAS/BMI_loh_scDRS_genes.in",
            row.names = F, quote = F, sep = "\t")
```

# Run scDRS v1.0.2

# Select top 1,000 genes and use z-score weights
scdrs munge-gs \
    --out-file /home/cbmr/mlf210/scDRS/GWAS/AD_bellenguez_weights_1000.gs \
    --zscore-file /projects/mludwig/hippo_GLP1/data/GWAS/AD_bellenguez_scDRS_genes.in \
    --weight zscore \
    --n-max 1000    


# Compute cell-specific scores
scdrs compute-score \
    --h5ad-file /home/cbmr/mlf210/scDRS/anndata_objs/hippo_labels.h5ad\
    --h5ad-species mouse\
    --gs-file /home/cbmr/mlf210/scDRS/GWAS/AD_bellenguez_weights_1000.gs\
    --gs-species human\
    --out-folder /home/cbmr/mlf210/scDRS/output\
    --flag-filter-data True\
    --flag-raw-count True\
    --n-ctrl 1000\
    --flag-return-ctrl-raw-score False\
    --flag-return-ctrl-norm-score True


# Compute cell-type-specific-scores
scdrs perform-downstream \
    --h5ad-file /home/cbmr/mlf210/scDRS/anndata_objs/hippo_labels.h5ad\
    --score-file /home/cbmr/mlf210/scDRS/output/AD.full_score.gz\
    --out-folder /home/cbmr/mlf210/scDRS/output\
    --group-analysis cell.type,cell.type2,drug\
    --gene-analysis\
    --flag-filter-data False\
    --flag-raw-count True


